Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-12-03 neurips-20/cvx-flats-scratch.tex
Adding COLT formatting files

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}

@@

\title{cvx-flats}

@@

\begin{abstract}
%	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
%	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
	In prediction tasks, one typically seeks to minimize \emph{empirical risk} by learning a hypothesis function making predictions from a given feature vector about a desired future outcome.
	This hypothesis is learned by minimizing a loss function over a set of labeled training data.
	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses that are ``efficient'' in the dimension of their input.
	We observe a connection between consistent surrogates and indirect property elicitation, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
	In particular, we characterize the minimal input dimension needed in order to construct a \emph{convex}, consistent surrogate using tools from property elicitation.
\end{abstract}

@@

In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
For example, 0-1 loss is often desired for classification tasks.
However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
In particular, we want our surrogate loss to yield guarantees so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss, regardless of the underlying data distribution.
Moreover, in continuous prediction settings, one often stats with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given property.
For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
Throughout this paper, the statistical guarantees we desire are \emph{consistency}.
In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any optimal prediction can be linked to either the correct prediction for the discrete loss or statistic value, depending on the setting.

We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
\cite{frongillo2015elicitation} poses an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is equivalent to finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.

In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{property elicitation} and \emph{consistency}.
We draw connections between the two in Section~\ref{sec:char-convex}, presenting our main result (Theorem~\ref{thm:cvx-flats},) a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
Our Theorem~\ref{thm:cvx-flats} generalizes their \emph{subspace of feasible dimensions}, and we can use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section 8]{frongillo2018elicitation}.

\subsection{Notation}
In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.

%discrete land
Let $\R$ be a (sometimes finite) report set and $\Y$ a outcome set; it is not necessary for $\Y = \R$.  
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
A loss $\ell : \R \times \Y \to \reals_+$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{original loss} for which we want to construct a consistent surrogate.
We denote $\ell(r)_y$ as the $y^{th}$ element of the vector $\ell(r)$, and consider this to be the punishment for reporting $r$ if outcome $y$ is realized.
For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
When considering surrogate losses, we denote the loss by $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.

Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions.
Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \P \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$, where $\P \subseteq \simplex$.
We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.

Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
Here, when we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \P$.
If $\P = \simplex$, this is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.

\section{Related work}\label{sec:related-work}
In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
Recently, the elicitation of multiple properties was studied by~\cite{frongillo2015vector-valued,frongillo2015elicitation,fissler2015higher}.
In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.

\subsection{Property elicitation}\label{subsec:properties}
Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.

@@

\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
When one starts with a discrete loss they want to minimize or property they want to learn, these are often computationally hard problems.
For this reason, we use surrogate losses to address these difficulties.
However, to measure the effectiveness of a surrogate loss, one needs a link function to map back to the original prediction space; moreover, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
This notion of a correct surrogate is captured by two slightly distinct notions introduced here: \emph{consistency} and \emph{calibration}.

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and ~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses, i.e. those where both the report and outcome set are finite.
They additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.

While the subtleties of \emph{consistency} vary slightly with each work, we use two definitions that have the same implications, but one may be more appropriate in a given context.

@@

For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense when we do not have one.
In this setting, we also define consistency with respect to a property that one wishes to estimate. 
\begin{definition}[Consistent: property]
	A loss $L : \reals^d \times \Y \to \reals$ is \emph{$d$-consistent with respect to a property} $\Gamma$ for a metric $d$ if, for all $D$ over $\X \times \Y$,  we observe
\begin{equation}
d(\E_X \Gamma(D_X), \Gamma(D)) \to 0 \implies \E_{(X,Y) \sim D} L(\E_X \Gamma(D_X), Y) \to \inf_{u \in \reals^d} \E_{(X,Y) \sim D} L(u, Y)~,~
\end{equation}
where $\Gamma(D) = \arginf_{u \in \reals^d} \E_D L(u, Y)$.
\end{definition}

One way to prove consistency of a surrogate loss  with respect to an original loss is to show that one has satisfied the following \emph{excess risk bound}.
\begin{definition}[Excess risk bound]
	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
	\begin{multline}
	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
	\end{multline}
\end{definition}

In finite settings, consistency and calibration of a surrogate are equivalent under mild assumptions.
Here, we generalize the definition of calibration to extend to continuous prediction settings.
\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}
	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
	\end{equation}
\end{definition}
In finite settings, the calibration is often given a more restrictive definition~\citet{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex,ramaswamy2018consistent}.
Their definition is given below, and we show in the Proposition~\ref{prop:calib-defs-equiv} that the general definition implies the following definition in finite settings.
\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}

\section{Characteristics of Consistent Convex Surrogates}\label{sec:char-convex}

@@

\begin{proposition}\label{prop:consistent-implies-indir-elic-loss}
	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\ell$, then $L$ indirectly elicits $\gamma := \prop{\ell}$.
\end{proposition}

\begin{proposition}\label{prop:consistent-implies-indir-elic-prop}
	If a surrogate and link pair $(L, \psi)$ is consistent with respect to $\gamma$, then $L$ indirectly elicits $\gamma$.
\end{proposition}

@@

@@

\begin{definition}[Flat]
	A \emph{flat} $F$ of $\reals^n$ is an affine subspace of $\reals^n$.
	In other words, $F\subseteq \reals^n$ can be written $F=\{x\in\reals^n : Wx + b = 0\}$ for some $W\in\reals^{d\times n}$ and $b\in\reals^d$ where $d\leq n$.
\end{definition}
The dimension of the flat $F$ is given by $f := n - \mathrm{rank}(W)$.
Unless otherwise mentioned, we will assume that $W$ is full rank so $f = n-d$.

@@

@@

\begin{theorem}[\cite{ramaswamy2016convex}]\label{thm:calib-iff-consistent}
	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \times \Y \to \reals_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
	\begin{equation*}
	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{equation*}
\end{theorem}
In words, a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.

@@

\newpage
\appendix
\section{Omitted proofs}
\begin{proposition}\label{prop:calib-defs-equiv}
	When $\R$ is finite, calibration of a property via Definition~\ref{calibrated-general} implies calibration via Definition~\ref{def:calibration-finite}.
\end{proposition}

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\prop}[1]{\mathrm{prop}[#1]}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{ccdim}}
\newcommand{\codim}{\mathrm{codim}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}
\newcommand{\propdis}{\mu}

@@

\title{Indirect elicitation as a necessary condition for consistent surrogate losses}

@@

\begin{abstract}
	\jessie{in other doc}
\end{abstract}

@@

In supervised machine learning, one often wants to make a prediction about future outcomes by training a classifier to minimize the average empirical loss of a labeled training set, where the loss is determined by the task at hand.
For example, 0-1 loss is often desired for classification tasks.
However, finite losses are typically difficult to optimize, so we construct a continuous \emph{surrogate} loss that one can more easily optimize.
In particular, we want our surrogate loss to yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for an original (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
Moreover, in continuous prediction settings, one often starts with a statistic of the data they would like to estimate, but it is often unclear how to construct a a loss that is consistent for the given statistic, or property.
For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
Throughout this paper, the statistical guarantees we desire are \emph{consistency}, as it is the only condition that guarantees good bounds on excess surrogate loss. \jessiet{Raf, maybe fill in here?}
In particular, we are specifically interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting.

We typically use convex surrogate loss functions that take some input $u \in \reals^d$ and measure error against the observed outcome $y \in \Y$.
The value $d$ provides some notion of efficiency for the surrogate, as low-dimensional convex losses can improve the efficiency of the optimization algorithm.
\cite{frongillo2015elicitation} pose an open question regarding a general characterization of the efficiency of \emph{convex elicitable properties}, which we show is bounded by finding the minimum dimension $d$ for which a consistent, convex loss can be constructed for the task at hand.

In Section~\ref{sec:related-work}, we review previous work and introduce the two main concepts used: \emph{consistency} and \emph{property elicitation}.
We draw connections between the two in Section~\ref{sec:consis-implies-indir} by showing that if a loss and link are consistent with respect to a target loss or the property it elicits, then it must also indirectly elicit the same property.
In Section~\ref{sec:char-convex}, we present our main result (Theorem~\ref{thm:cvx-flats}), a corollary of which characterizes the existence of consistent convex surrogates in a given dimension $d$.
In Section~\ref{sec:finite-calib}, we relate our setting to the study of \emph{convex calibration dimension} introduced by~\cite{ramaswamy2016convex} by focusing on the finite prediction setting.
Our Theorem~\ref{thm:cvx-flats} generalizes their bound on convex calibration dimension by observing that the \emph{subspace of feasible dimensions} constructed in their bound is just one case of a flat produced by our Theorem~\ref{thm:cvx-flats}.
To see this we use our results to generalize and simplify the proof of~\cite[Theorem 16]{ramaswamy2016convex}.
In continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
In Section~\ref{sec:contin-consis}, we address the construction of convex consistent losses by applying the main insights from Theorem~\ref{thm:cvx-flats} to this setting, answering the open question posed by~\cite[Section 8]{frongillo2018elicitation}.

\subsection{Notation}
\jessie{$\supp$, $\spn$}
In this paper, we take the outcome set $\Y$ and consider $\simplex$ to be the simplex over $\Y$.

%discrete land
Let $\R$ be a report set and $\Y$ a outcome set; it is not necessary for $\Y = \R$.  
For example, in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.
A loss $\ell : \R \times \Y \to \reals_+$ is a \emph{discrete loss} if $|\R| < \infty$, and in general, we use $\ell$ to denote our \emph{target loss} for which we want to construct a consistent surrogate.
For a distribution $p \in \simplex$, we denote the expected discrete loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
When considering surrogate losses, we denote the loss by $L : \reals^d \times \Y \to \reals_+$, and typically denote a surrogate report with $u$.

Throughout this paper, we use tools from \emph{property elicitation} to understand the existence of consistent surrogate functions; a property is simply a function mapping distributions over the outcome simplex to reports.
Introduced in Section~\ref{subsec:properties}, a property $\Gamma: \simplex \to 2^\R \setminus \emptyset$ is denoted $\Gamma:\P \toto \R$.
We call a property \emph{set-valued} if there is a $p \in \P$ so that $|\Gamma(p)| > 1$, and \emph{single-valued} otherwise.
We use $\Gamma := \prop{L}$ to denote that $\Gamma$ is the (unique) property elicited by $L$.

Throughout this paper, we focus on characteristics of \emph{convex} surrogate losses.
Here, when we say a loss $L(\cdot; p)$ is \emph{convex}, we mean that it is convex in its first argument for every $p \in \simplex$, which is equivalent to saying $L$ is convex in the report for every outcome $y \in \Y$.
Moreover, the regret of a loss $L(u; p)$ is the excess loss over the optimal.  
That is, $R_L(u,p) := L(u,p) - \inf_{u^*} L(u^*, p)$.

\section{Related work}\label{sec:related-work}
\subsection{Consistency and calibration for convex losses}\label{subsec:convex-surrogates}
When one starts with a discrete loss they want to minimize, it is often a computationally hard problem.
For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss (or property we want to predict).
However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the original prediction space.
In particular, we would like to map back to the \emph{correct} prediction that would have been given if we had directly optimized the original problem.
This notion of a correct surrogate is captured by two slightly distinct notions introduced here: \emph{consistency} and \emph{calibration}.

\cite{zhang2004statistical,lin2004note,bartlett2006convexity,tewari2007consistency} form a characterization of consistent and calibrated surrogates for classification problems.
In particular,~\cite{bartlett2006convexity} show that if a convex surrogate is differentiable, minimal at $0$, and nonnegative, there is a consistent surrogate for binary classification problems, and~\cite{tewari2007consistency} generalizes this result for multiclass classification. 
\cite{ramaswamy2016convex} further show necessary and sufficient conditions for finite prediction problems to be consistent that can be applied to general discrete losses.
They additionally introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for finite prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.

%One way to prove consistency of a surrogate loss  with respect to an original loss is to show that one has satisfied the following \emph{excess risk bound}.
%\begin{definition}[Excess risk bound]
%	A surrogate loss and link pair $(L,\psi)$ satisfies the \emph{excess risk bound} with respect to a loss $\ell$ if there exists an increasing function $\zeta : \reals \to \reals$ that is continuous at $0$ with $\zeta(0) = 0$ so that for all $f:\X \to \R$ and data distributions $D$ over $\X \times \Y$, we have
%	\begin{multline}
%	\E_{(X,Y) \sim D} \ell(\psi \circ f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} \ell(\psi \circ f^*(X), Y) \\ 
%	\leq \zeta \left( \E_{(X,Y) \sim D} L(f(X), Y) - \inf_{f^*} \E_{(X,Y) \sim D} L(f^*(X), Y) \right)
%	\end{multline}
%\end{definition}

In finite settings, calibration as given in Definition~\ref{def:calibrated-finite} has been shown to be equivalent to consistency~\citet{bartlett2006convexity,tewari2007consistency,ramaswamy2016convex,ramaswamy2018consistent}.
\begin{definition}[Calibrated: Finite predictions]\label{def:calibrated-finite}
	Let $\ell : \R \times \Y \to \reals_+$ be a discrete loss eliciting the property $\gamma$.
	A surrogate loss $L : \reals^d \times \Y \to \reals_+$ is \emph{calibrated} with respect to $\ell$ if there exists a link function $\psi: \reals^d \to \R$ such that
	\begin{equation}\label{eq:calibration}
	\forall p \in \simplex: \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p)~.~
	\end{equation}
\end{definition}
In Appendix~\ref{app:calibration}, we give a more general definition of calibration which implies this definition in finite outcome settings.

\subsection{Property elicitation}\label{subsec:properties}
In this paper, we use tools from property elicitation to study the construction of consistent surrogate losses.
Property elicitation of a single property is well-understood through \cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting, lambert2009eliciting, lambert2018elicitation}.
Recently, the elicitation of multiple properties was studied by~\cite{frongillo2015vector-valued,frongillo2015elicitation,fissler2015higher}.
In particular, these works study the \emph{minimum} dimension of a real-valued loss needed to elicit a property or vector of properties.
Moreover,~\cite{agarwal2015consistent} is the first to our knowledge to formally relate property elicitation to the consistency of a surrogate loss.

Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.

@@

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
While the subtleties of \emph{consistency} vary slightly with each work, we use two definitions that have the same implications, but one may be more appropriate in a given context.

@@

For continuous properties, such as the expected value, variance, and entropy, asking for a consistent surrogate with respect to an original \emph{loss} may not make sense when we do not have one.
In this setting, we also define consistency with respect to a property that one wishes to estimate. 
\begin{definition}[Consistent: property]
	Blah blah
\end{definition}

@@

\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
	\raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
\end{proposition}

\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}

@@

\begin{theorem}\label{thm:consistent-implies-indir-elic}
	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{theorem}

\section{Characteristics of Consistent Convex Surrogates}

@@

\begin{definition}[Flat]
	blah blah
\end{definition}
The codimension of the flat $F$ is given by $f := \mathrm{rank}(W)$.

@@

\begin{definition}[Subspace of feasible directions]
	Define the \emph{subspace of feasible directions} $\S_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ as the subspace $\S_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
	%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
\end{definition}

\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the finite elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\S_{\gamma_r}(p)$.
	%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
	To spell it out, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
	Now consider $v \in F - p$.
	Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
	Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
	%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
	%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
	%  
	%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \S_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
	%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
	%  Therefore, we have $v \in F - p \implies v \in \S_{\gamma_r}(p)$, so $(F - p) \subseteq \S_{\gamma_r}(p)$.
\end{proof}

%\begin{lemma}\label{lem:feas-sub-is-a-flat}
%	Suppose we have the finite property $\gamma$ and distribution $p \in \simplex$.
%	For ant $r$ such that $r \in \gamma(p)$, the subspace $F := \mu_{\gamma_r}(p) + p $ is a flat, $F$ contains $p$, and $F \cap \simplex \subseteq \gamma_r$.
%\end{lemma}
%\begin{proof}
%	Write the level set $\gamma_r = \{q \in \reals^n : A_1 q \leq b_1, \; A_2 q \leq b_2, \; A_3 q \leq b_3 \}$, where $A_1 p \leq b_1, A_2 p < b_2,$ and $A_3 p = b_3$.
%	
%	We want to show three things: first, $F$ is a flat as it is $\ker([A_1 ; A_3])$ by~\cite{ramaswamy2016convex}.
%	Second, $p \in F + p$ by construction, since $\vec 0 \in F$.
%	(Consider that $p \in \gamma_r$, so with $epsilon_0 = 1$, we have $p + \epsilon\vec 0 = p \in \gamma_r$ for all $\epsilon \in (0, 1)$; thus, $\vec 0 \in F$.)
%	
%	Third, we want to show $(F + p) \cap \simplex \subseteq \gamma_r$.
%	Take some $q := p + \epsilon v$ for $v \in F$.
%	By construction of $F$, we have $q \in F \implies q \in \simplex$, so $F + p \subseteq \simplex \implies F + p \cap \simplex = F + p$.
%	Thus it just remains to be shown that $F + p \subseteq \gamma_r$.
%	Since $v\in F \implies q \in F + p \implies p + \epsilon v \in \gamma_r$ by construction, so we have $F+p \subseteq \gamma_r$.	
%\end{proof}

%\begin{lemma}\label{lem:p-boundary-fstar}
%	For a given property $\gamma$, fix $p \in \simplex$ and $r \in\R$ so that $r \in \gamma(p)$.
%	Consider the flat $F'$ containing $p$ of dimension at least $n-d-1$.
%	The flat $F^* = F' \cap \spn(\{e_y : y \in \supp(p)\})$ has dimension $\dim(F') - (n - \|p\|_0)$.
%\end{lemma}
%\begin{proof}
%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
%	\begin{align*}
%	\dim(F^*) &= \dim(F') + \|p\|_0 - \dim(F' + P)
%	\end{align*}
%	The claim then holds if $n = \dim(F' + P)$.
%	\jessie{This is where I'm stuck??}
%\end{proof}

\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \simplex$ and $r$ such that $p \in \gamma_r$, define $\gamma'$ to be $\gamma$ restricted to the simplex $\Delta_{\supp(p)}$.
	Then $\S_{\gamma_r}(p) = \S_{\gamma'_r}(p)$.
\end{lemma}

@@

\begin{corollary}[\cite{ramaswamy2016convex}]\label{thm:calib-iff-consistent}
	If $\Y$ is finite, then the surrogate loss $L:\reals^d \to \reals^\Y_+$ is calibrated with respect to $\ell: \R \times \Y \to \reals_+$ if and only if there exists a link function $\psi : \reals^d \to \R$ such that for all distributions $D$ on $\X \times\Y$ and all sequences of (vector) functions $f_m : \X \to \reals^d$,
	\begin{equation*}
	\E_D L(f_m(X), Y) \to \inf_f \E_P L(f(X), Y) \implies \E_D \ell(\psi  \circ f_m(X), Y) \to \inf_f \E_D \ell(\psi \circ f(X), Y)~.~
	\end{equation*}
\end{corollary}
In words, a surrogate and link are calibrated with respect to a discrete loss if and only if any consistent sequence of hypotheses for the surrogate, when linked, is consistent for the discrete loss.

@@

\newpage
\appendix
\section{A case for general calibration}

In finite settings, consistency and calibration of a surrogate are equivalent under mild assumptions.
Here, we generalize the definition of calibration to extend to continuous prediction settings.
\begin{definition}[Calibrated]\label{def:calibrated-general}
	A loss $L:\reals^d \times \Y \to \reals$ is \emph{calibrated} with respect to a property $\gamma : \simplex \toto \R$ elicited by the loss $\ell$ if there is a link $\psi : \reals^d \to \R$ such that, for all distributions $p \in \simplex$, there exists an increasing function $\zeta : \reals \to \reals$ with $\zeta$ continuous at $0$ and $\zeta(0) = 0$ such that for all $u \in \reals^d$, we have
	\begin{equation}
	\ell( \psi(u); p) - \ell(\gamma(p); p)  \leq \zeta \left(  L(u;p) - L(\Gamma(p); p) \right)~.~
	\end{equation}
\end{definition}

\begin{proposition}\label{prop:calib-defs-equiv}
	When $\R$ is finite, calibration of a property via Definition~\ref{calibrated-general} implies calibration via Definition~\ref{def:calibration-finite}.
\end{proposition}
